---
title: "Programming Background"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="../images/")
```

```{r, eval=FALSE}
# Working directory is /Users/Blog but for some reason the render function is looking into the _Rmd folder

rmarkdown::render(
    '2022-06-03-programming-background.Rmd', 
    output_format = "github_document",
    output_dir = "../_posts",
    output_options = list(
      html_preview = FALSE
    )
)
```

## Background

Coming from a .NET background, using languages like R is a bit different since there is no compilation step and, because of that, no type checking. A part of me likes this since the type checking can be helpful to find errors as early as possible in the development process.

However, with interpretable languages like R more and more tools are becoming available that make it easier to spot similar types of errors. R Studio gets better every day so it's getting better to find errors early on in development.

While R isn't a hard language to learn, in fact, I'd say it's one of the easier ones, getting started with it has become a lot easier. Since Jupyter and RStudio have come a lot, getting started has become so easy you can start coding with a Chromebook and a book on R.

## Example R Output

```{r, eval=TRUE}
plot(ToothGrowth)
```

