---
title: "R Thoughts"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE, echo=FALSE}
rmarkdown::render(
    '2022-06-30-r-thoughts.Rmd', 
    output_format = "github_document",
    output_dir = "../_posts",
    output_options = list(
      html_preview = FALSE
    )
)
```

# R Thoughts

After doing some programming and a project in R, I feel I have a decent amount of experience to go over some thoughts of the language as a whole. Mostly, it's a very nice language to use. The base packages has a lot of what you would need to get started doing statistical analysis and the CRAN network has a lot of packages that others have written to do even more. 

One of the coolest packages is probably the "tidyverse" package, which includes several packages for data analysis, such as readr for reading in files or dplyr for data manipulation. For example, dplyr can do a lot in terms of data manipulation.

```{r}
library(tidyverse)

ToothGrowth %>%
  as_tibble() %>%
  filter(length >= 10 & dose < 2.0)
```

Another nice thing about R is that is has a great IDE for it - R Studio. This IDE does a lot including helping to knit R Markdown documents and has a built-in visualizer for plots.